\thispagestyle{empty}
\vspace{-3cm}
\section*{\centering Acknowledgements}
\bigskip
After the quest is over, I wish to sincerely thank all the people,
without whom this work would never have been accomplished.

\smallskip
First of all, thanks goes to {\bf Olaf Behnke}, the driving force behind the heavy flavour measurement part of this thesis.
Thank you, Olaf, for all your constant support and encouragement!
Your enthusiasm was always motivating, your experience was invariably guiding the way, your jokes were repeatedly helping in tough moments!

\smallskip
On the hardware side of the thesis, I would like to thank {\bf Ingrid-Maria Gregor}.
Thanks, Ingrid, for introducing me into the world of Particle Detectors and for giving me an opportunity to work on the ATLAS Pixel beam test program!
You were always providing a lot of inspiration and stimulation to work hard, but it was always a lot of fun as well!

\smallskip
A number of people supported me in the course of these studies, whom I am very much pleased to thank here:
\begin{itemize}
 \item {\bf Prof.~Robert Klanner} -- for critically reviewing the work and for providing valuable comments on the manuscript;
 \item {\bf Philipp Roloff} -- for introducing me into the secondary vertex analysis and for tremendous help at initial stages of the work;
 \item {\bf Achim Geiser} -- for deep involvement in the analysis at all stages;
 \item {\bf Sasha Viazlo} -- for his dedicated Monte Carlo studies;
 \item {\bf Ulrich K\"otz} -- for providing the right guidance and equipment in the laboratory;
 \item {\bf J\"org Behr} -- for help with the EUTelescope software;
 \item {\bf Igor Rubinsky}, {\bf Jens Weingarten}, {\bf Matthias George} and everyone from the ATLAS Planar Pixel and IBL test beam groups -- for nice team work on ATLAS pixels;
 \item ZEUS Heavy Flavour group and DESY-Pixel group -- for many fruitful discussions.
\end{itemize}

Special acknowledgement to {\bf Vladimir Y. Aushev} who back in 2007 proposed me to work on the ZEUS experiment for my bachelor thesis, and thus opened to me the doors of Particle Physics!
\smallskip

Time to recall {\bf my friends} -- my colleagues here at DESY as well as my ``old'' friends in the fatherland -- thanks for a lot of fun during these years!
\smallskip

Finally, I am so happy to express heartfelt gratitude to {\bf my lovely family}.
Not to speak that your steady support and firm trust helped me all the way to finish this work -- it's fair to say that I would never become a physicist without you!
\vspace{\baselineskip}

{\bf THANK YOU ALL! }